% Paper 2 - Methods
% Camera-ready draft from Kelly

\subsection{Model}
The stochastic Kuramoto model is a canonical system in synchronization
theory~\cite{kuramoto1984chemical,strogatz2000kuramoto,acebron2005kuramoto},
making it a natural platform for exploring CHSH-like geometries.
We study a pair of bidirectionally coupled phase oscillators governed by
stochastic Kuramoto dynamics~\cite{kuramoto1984chemical,sakaguchi1986soluble},
\begin{align}
  \dot{\theta}_1 &= \omega_1 + K \sin(\theta_2 - \theta_1) + \sigma\,\xi_1(t),\\
  \dot{\theta}_2 &= \omega_2 + K \sin(\theta_1 - \theta_2) + \sigma\,\xi_2(t),
\end{align}
where $(\theta_1,\theta_2)\in[0,2\pi)$ are phases, $K$ is coupling strength,
$\sigma$ is additive Gaussian noise amplitude, and $\xi_i(t)$ are independent
Wiener processes with variance $2\,\mathrm{d}t$.  Unless noted otherwise we set
$\omega_1=1.0$, $\omega_2=1.0+\Delta\omega$ with $\Delta\omega=0.2$.  Dynamics
are integrated with the Euler--Maruyama method using timestep $\mathrm{d}t=
0.01$ for $T=6\times 10^5$ steps, with the first $3\times10^5$ discarded as
transient.

We explore a rectangular grid in the $(K,\sigma)$ plane.  Coupling is sampled
uniformly from $K\in[0.10,1.00]$ in 19 steps; noise from
$\sigma\in[0.00,0.60]$ in 21 steps unless otherwise noted.  Each configuration
is repeated for $5$ independent random seeds.

\subsection{Continuous-phase CHSH functional}
At each sampling time $t$ we evaluate a continuous-phase version of the CHSH
functional~\cite{clauser1969proposed},
\begin{equation}
  S(t) = E(a,b) - E(a,b') + E(a',b) + E(a',b'),
\end{equation}
where $a,a',b,b'$ are measurement angles and
\begin{equation}
  E(x,y) = \cos(\theta_1(t)-x)\,\cos(\theta_2(t)-y).
\end{equation}
In Paper~1 we showed that $(a,a',b,b')=(0^\circ,98^\circ,45^\circ,127^\circ)$
maximizes $|S|$ in the deterministic limit.  Unless stated otherwise, these
angles are used for all instantaneous and temporal measurements in Paper~2.
Angle-resolved scans (Section~\ref{sec:angle_field}) search the full
$31^4$-grid of angles with coarse-to-fine refinement to identify optimal
settings at each $(K,\sigma)$ point.

Instantaneous $S$ is computed every $100$ integration steps.  Time-averaged
values $\langle|S|\rangle$ are obtained from the final $3\times10^5$ steps
after the transient period.

\subsection{Temporal correlation and memory measures}
To study temporal persistence we compute the lag-resolved correlation,
\begin{equation}
  \rho_S(\tau) = \mathrm{corr}[S(t), S(t+\tau)],
\end{equation}
for $\tau\in\{10,25,50,100\}$ sampling intervals.  The primary memory statistic
used in this paper is $\rho_S(50)$, which provides a mid-range probe of
correlation persistence and separates the coherent ridge from the intermediate
band and noise basin.

To quantify curvature of correlation decay, we fit a three-point local
parabolic model to the lag sequence $\{\rho_S(10), \rho_S(25), \rho_S(50),
\rho_S(100)\}$, yielding the midpoint curvature $C_{\mathrm{mem}}$:
\begin{equation}
 C_{\mathrm{mem}} = \frac{\rho_S(\tau-\Delta) - 2\,\rho_S(\tau)
                     + \rho_S(\tau+\Delta)}{\Delta^2},
\end{equation}
evaluated at the midpoint $\tau=37.5$ with $\Delta=12.5$.  Positive curvature
indicates echo growth at mid-lag, while negative curvature indicates decaying
temporal coherence.

\subsection{Directional susceptibility \texorpdfstring{$\chi$}{chi} (formerly recursive susceptibility)}
We define a susceptibility-like quantity that measures the sensitivity of the
CHSH field to small changes in measurement geometry.  For a shift
$\delta a=1^\circ$ we compute
\begin{equation}
  \chi = \frac{S(a+\delta a,a',b,b') - S(a,a',b,b')}{\delta a},
\end{equation}
and average over time.  This directional derivative captures how the CHSH
surface bends under perturbations of measurement angle.  In practice we use
central differencing to improve stability.

\subsection{Memory-collapse threshold}
The \emph{memory threshold} $\sigma_{\mathrm{mem}}$ is defined as the smallest
noise level at which mid-lag memory satisfies
\begin{equation}
  \rho_S(50) < 0.05,
\end{equation}
a conservative threshold below the noise floor of random sequences of similar
length.  The collapse boundary $\sigma_{\mathrm{mem}}(K)$ is identified by
linear interpolation between the last noise value with $\rho_S(50)\ge 0.05$
and the first with $\rho_S(50)<0.05$.  High-resolution scans use noise steps of
$0.002$ to resolve the catastrophic collapse observed in Section~3.1.

\subsection{Angle-resolved field geometry}
\label{sec:methods-angle}
For each $(K,\sigma)$ coordinate we search the $(a,a',b,b')$ space for the
angles that maximize $\langle|S|\rangle$.  We first evaluate $S$ on a coarse
$31^4$ grid (6.2M angle combinations), then refine within a $10^\circ$
hypercube surrounding the best configuration using $1^\circ$ resolution.  This
produces a vector field of optimal orientations across the $(K,\sigma)$ plane,
from which we compute angle gradients, shear fields, and the orientation
flow shown in Section~\ref{sec:angle_field}.

\subsection{Software and reproducibility}
All simulations in this work were performed using a fully scripted,
version-controlled workflow. The oscillator dynamics, CHSH evaluation,
temporal-memory metrics, and field-geometry analyses are implemented in
standalone Python modules with no manual manipulation between stages. Each
experiment (E201--E231) is specified by a JSON configuration file defining all
parameters (time horizon, timestep, coupling values, noise levels, measurement
angles, and random seeds). Executing a configuration produces a complete run
manifest recording the input parameters, parameter-hash, software versions,
and all generated outputs.

For every figure, the raw data, intermediate arrays (e.g., autocorrelation
curves, curvature maps, and angle-optimized fields), and plotting scripts are
stored alongside the corresponding experiment directory, enabling exact
regeneration of all panels. The CHSH and echo metrics were validated by
independent control tests (deterministic $\sigma=0$ limit, noise-only $K=0$
regime, and coupling-null baseline from Paper~1), and all numerical routines
were benchmarked for timestep stability. Random seeds are fixed across all
sweeps, ensuring that rerunning any experiment produces bitwise-identical
output.

The entire workflow---from simulation to figure generation---is executed
through reproducible shell scripts (e.g., \texttt{RUN\_ALL\_P2\_WARMUP.sh})
that rebuild every result from a clean environment. Together, these components provide full computational
transparency and allow every result in this paper to be reproduced exactly on
any standard Python installation.
