\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\setlength{\parskip}{0pt}
\usepackage{physics}
\usepackage{titlesec}
\usepackage{tocloft}

% Equation spacing
\setlength{\abovedisplayskip}{10pt}
\setlength{\belowdisplayskip}{10pt}

% Section header formatting
\titleformat{\section}{\normalsize\normalfont\bfseries\Large}{\thesection}{1em}{}[\normalsize]
\titleformat{\subsection}{\normalsize\normalfont\bfseries\large}{\thesubsection}{1em}{}[\normalsize]
\titleformat{\subsubsection}{\normalsize\normalfont\bfseries}{\thesubsubsection}{1em}{}[\normalsize]

% TOC formatting
\cftsetpnumwidth{2em}
\cftsetrmarg{3em}

\title{CHSH Memory in Small Oscillator Networks:\\
Topology, Interference, and Collective Echo\\[10pt]
\large Paper 3: Network Motifs}
\author{Kelly McRae}
\date{December 2025}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\begin{document}
\normalfont
\maketitle

\begin{abstract}
% PLACEHOLDER - To be written
Papers~1 and~2 established the CHSH landscape and its temporal structure for a
driven two-oscillator system. Here we extend the analysis to three-oscillator
networks, examining how topology shapes CHSH memory. We study three canonical
motifs---chain, star, and triangle---and characterize their echo surfaces,
curvature profiles, and susceptibility maps. The chain topology exhibits
end-to-end memory decay with a characteristic length scale. The star motif
shows hub-dominated correlations with spoke-to-spoke interference. The triangle
configuration displays cyclic memory flow and topology-dependent phase
structure. Across all motifs, the universal memory threshold
$\sigma_{\mathrm{mem}}\approx 0.002$ persists, confirming its independence from
network structure. These results complete the trilogy by demonstrating that
CHSH memory is a topological observable whose geometry reflects the underlying
coupling graph.
\end{abstract}

\newpage
\tableofcontents
\newpage


%=============================================================================
\section{Introduction}
%=============================================================================

\input{sections/introduction}


%=============================================================================
\section{Methods}
%=============================================================================

\input{sections/methods}


%=============================================================================
\section{Results}
%=============================================================================

% Section 3.1 - Chain Topology
\input{sections/results_3_1_chain}


% Section 3.2 - Star Topology
\input{sections/results_3_2_star}


% Section 3.3 - Triangle Topology
\input{sections/results_3_3_triangle}


% Section 3.4 - Cross-Topology Comparison
\input{sections/results_3_4_comparison}


% Section 3.5 - Synthesis
\input{sections/results_3_5_synthesis}


%=============================================================================
\section{Discussion}
%=============================================================================

\input{sections/discussion}


%=============================================================================
\section{Conclusion}
%=============================================================================

\input{sections/conclusion}


%=============================================================================
% References
%=============================================================================

\bibliographystyle{unsrt}
\bibliography{bib/references}


%=============================================================================
% Appendices (if needed)
%=============================================================================

% \appendix
% \input{sections/appendix}


\end{document}
