\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{mathptmx}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{parskip}
\setlength{\parindent}{15pt}
\setlength{\parskip}{0pt}
\usepackage{physics}
\usepackage{titlesec}
\usepackage{tocloft}

% Equation spacing
\setlength{\abovedisplayskip}{10pt}
\setlength{\belowdisplayskip}{10pt}

% Section header formatting
\titleformat{\section}{\normalsize\normalfont\bfseries\Large}{\thesection}{1em}{}[\normalsize]
\titleformat{\subsection}{\normalsize\normalfont\bfseries\large}{\thesubsection}{1em}{}[\normalsize]
\titleformat{\subsubsection}{\normalsize\normalfont\bfseries}{\thesubsubsection}{1em}{}[\normalsize]

% TOC formatting
\cftsetpnumwidth{2em}
\cftsetrmarg{3em}

\title{Echo Geometry of the Classical CHSH Ridge:\\
Memory, Curvature, and Directional Susceptibility\\[10pt]
\large Paper 2: The Memory Landscape}
\author{Kelly McRae}
\date{December 2025}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
}

\begin{document}
\normalfont
\maketitle

\begin{abstract}
Paper~1 showed that a pair of deterministically coupled oscillators exhibits a
well-defined CHSH landscape: a high-$|S|$ ridge at low noise and a sharp
collapse boundary at $\sigma_{\mathrm{c}}(K)$. Here we extend this analysis by
resolving the \emph{temporal structure} of CHSH correlations across the full
$(K,\sigma)$ plane. Using lag-resolved correlation decay, curvature,
susceptibility, and angle-dependent scanning, we identify three robust regimes.
(1) A trivial noise-dominated basin in which $|S|<2$ and all memory measures
vanish. (2) A structured intermediate band where $|S|>2$ persists but
long-lag memory has already collapsed, marked by a shallow mid-range
enhancement in $\rho_S(\tau)$ and a complex pattern of positive and negative
curvature. (3) A narrow ridge of strong instantaneous coherence in which
$|S|\approx 2.8$ but temporal persistence remains extremely fragile. Across the
entire domain we find a universal memory threshold
$\sigma_{\mathrm{mem}}\approx 0.002$, two orders of magnitude below the CHSH
collapse curve, beyond which long-lag CHSH memory cannot be sustained for any
choice of angles, confirming that memory collapse reflects intrinsic
relative-phase dynamics rather than discretization or finite sampling.

We further treat the CHSH functional as a directional field by scanning across
all measurement geometries. The resulting angle-resolved surfaces show that
the optimal CHSH configuration twists under noise, exhibiting multiple
susceptibility sign changes and a well-defined angle-flow structure. Evaluated
at these optimal angles, long-lag memory still collapses at the universal
threshold, confirming that temporal coherence is limited by intrinsic dynamics
rather than geometry. Together, these results show that the CHSH ridge is a
multi-layered temporal object whose instantaneous and lagged correlations are
governed by distinct noise scales. This temporal decomposition provides the
framework used in Paper~3 to analyze CHSH-like memory in small oscillator
networks.
\end{abstract}

\newpage
\tableofcontents
\newpage


%=============================================================================
\section{Introduction}
%=============================================================================

\input{sections/introduction}


%=============================================================================
\section{Methods}
%=============================================================================

\input{sections/methods}


%=============================================================================
\section{Results}
%=============================================================================

% Section 3.1 - Camera-ready draft
\input{sections/results_3_1_memory_threshold}


% Section 3.2 - Camera-ready draft
\input{sections/results_3_2_curvature}


% Section 3.3 - Camera-ready draft (includes echo + χ surfaces)
\input{sections/results_3_3_echo}


% Section 3.4 - Synthesis: Three Regimes
\input{sections/results_3_4_chi}


% Section 3.5 - Angle-Resolved Observer Field
\input{sections/results_3_5_angle_field}


%=============================================================================
\section{Discussion}
%=============================================================================

\input{sections/discussion}


%=============================================================================
\section{Conclusion}
%=============================================================================

\input{sections/conclusion}


%=============================================================================
% References
%=============================================================================

\bibliographystyle{unsrt}
\bibliography{bib/references}


%=============================================================================
% Appendices (if needed)
%=============================================================================

% \appendix
% \input{sections/appendix}


\end{document}
