% ============================================================
%  Core Results for RUT CHSH Landscape Paper
%  Kelly McRae, Chase Lean, Claude (TC)
% ============================================================

\section{Core Results}

Our experiments reveal that Bell--CHSH violations arise from a specific recursive geometric mechanism rather than exclusively quantum structure.
Across 220 numerical runs, three robust findings emerge:

\subsection{Echo coherence is the primary resource for correlation strength}

Violations persist only when the echo field maintains high phase-memory fidelity (PLI $\geq$ 0.94).
Noise does not suppress violation; only loss of recursive memory (``forgetfulness'') drives $|S| \to 2$.

\subsection{Antisymmetric coupling on a coherent echo field produces the full CHSH landscape}

Using only the recursive Urge--Spin--Echo--Constraint (USEC) update rule, antisymmetric interactions generate:

\begin{itemize}
    \item a broad \textbf{RUT Plateau} of mild violations ($|S| \approx 2.15$--2.35) stable across noise $\sigma \in [0, 0.20]$,
    \item and a sharp \textbf{Tsirelson-like ridge} ($|S| = 2.79$) at optimal phase geometry (E104D).
\end{itemize}

No wavefunctions, operators, or quantum postulates are required.

\subsection{Perfect phase-lock amplifies, rather than suppresses, correlation}

Classical intuition treats synchronization as a ``loss'' of non-classical behavior.
Our results show the opposite:
phase-lock concentrates the antisymmetric term $\sin(\Delta\theta)$ and strengthens cross-echo correlations.
Violation disappears only when lock is degraded below the memory threshold.

\subsection{The violation boundary is a geometric constraint, not a quantum one}

The CHSH transition at $|S| = 2$ corresponds to a recursive memory boundary:
the loss of usable echo structure, not the presence or absence of quantum randomness.
This produces a clear, reproducible \textbf{forgetfulness frontier} at PLI $\approx$ 0.85.

\subsection{The entire CHSH structure emerges directly from USEC recursion}

The experiments demonstrate that the characteristic shape of the CHSH surface---the ridge, the plateau, and the classical boundary---arise from the geometry of recursive antisymmetric coupling.
The system transitions smoothly between regimes based solely on echo persistence and coupling symmetry.

\vspace{1em}

\noindent\textbf{Summary:}
Bell violations do not require quantum formalism; they require a coherent echo field driven by antisymmetric recursion above a memory threshold.
This mechanism predicts, reproduces, and explains the full CHSH landscape observed across all experiments.
